\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-10 paper/main.tex
.

In history, traditional remedies, that were known for their medicinal
properties lead to drugs by extraction of the functional
ingredients. Alternatively, characteristics and features of potential
drugs were detected by accident like in the case of penicillin. More
recently, biological drug targets can be found \textit{in silico}
through discovery of suitable computational predictors.

The challenge of accurately predicting drug-target-interactions (DTI)
has shown its importance in the fields of drug repurposing and
repositioning, and in the exploration of novel drugs and their
interaction partners. Knowledge about those links between compounds
and their target proteins help in an array of medical and
pharmaceutical studies. Additionally, those associations can be
utilized to identify disease specific targets, leading to desirable
therapeutic effects.

With the rapidly growing field of machine learning approaches and
their application to bioscientifical problems in the realm of
bioinformatics, different kinds of data, such as long DNA sequences
could be utilized for feature generation, while rapid advances were
made.

@@

These approaches can be classified into top-down and bottom-up methods. Top-down or network approaches hereby start form the observable, phenotypical characteristics, such as side-effects, associated diseases and indications represented by knowledge graphs or ontologies, induced by a drug and infer targets based on the likely molecular mechanisms that result in these phenotypes. On the other hand, bottom-up approaches start from molecular features, such as molecular structure, molecular fingerprints, secondary structure and contact predictions and others, deriving predictions from suitable correlations between these features.

However, both bottom--up and top--down approaches to drug--target interaction prediction contain some limitations that are not solvable within themselves. Generally, it is very challenging for bottom-up methods to accurately predict, whether there a structure is binding to a protein, as not only molecular structure, but also binding sites and molecular forces are crucial for accurate prediction. Thus, finding similarities for dissimilar drugs affecting the same targets is problematic but crucial. Furthermore, phenotypic features contain relevant information for DTI prediction \cite{Campillos2008} that are complementary to knowledge gained from molecular properties. While bottom-up representations possibly contain all information needed for accurate DTI prediction, we rely on indirect information for better generalization. Contrary, top-down approaches lack the ability to spot and cope with small differences within the molecular drug structure, thus both incapable to predict on novel entities and derive similarity from structural correlation.

>>>>

% In history, traditional remedies, that were known for their medicinal
% properties lead to drugs by extraction of the functional
% ingredients. Alternatively, characteristics and features of potential
% drugs were detected by accident like in the case of penicillin. More
% recently, biological drug targets can be found \textit{in silico}
% through discovery of suitable computational predictors.

% Knowledge about those links between compounds and their
% target proteins help in an array of medical and pharmaceutical
% studies. Additionally, those associations can be utilized to identify
% disease specific targets, leading to desirable therapeutic effects.

% With the rapidly growing field of machine learning approaches and
% their application to bioscientifical problems in the realm of
% bioinformatics, different kinds of data, such as long DNA sequences
% could be utilized for feature generation, while rapid advances were
% made. 
Identifying drug--target interactions (DTIs) is important in drug
repurposing and repositioning, and in the exploration of novel drug
candidates and their interaction partners. Computational methods are
widely applied to predict DTIs and many computational methods have
been developed.  These methods can be broadly classified into
``top-down'' and ``bottom-up'' approaches. Top-down approaches start
form observable characteristics resulting from a drug--target
interaction, such as side-effects or the diseases treated by a drug,
and infer likely molecular mechanisms (i.e., the interaction) using
these observations.
% and indications represented by knowledge graphs or ontologies, induced by a drug and infer targets based on the likely molecular mechanisms that result in these phenotypes
Bottom-up approaches start from molecular features such as molecular
structure or fingerprints associated with drug and protein, and
predict interactions from this information.

Both bottom-up and top-down approaches to drug--target interaction
prediction have some advantages and limitations. Generally, bottom-up
methods face the challenge to predict whether a structure binds to a
protein given their molecular properties; whether two entities
interact depends not only on the molecular structure of the entities
(where binding sites and molecular forces need to be determined for
accurate prediction) but also properties such as where a protein is
expressed or in which celltypes and anatomical structures. Top-down
methods use information for DTI prediction such as side-effect
similarity \cite{Campillos2008} that is largely complementary to
knowledge gained from molecular properties. While methods that rely on
molecular information are directly predicting whether two molecular
could interact, top-down methods rely on more indirect means and 
infer a DTI from observable effects resulting from the interaction.

Both approaches may be used in conjunction with network inference
\cite{}.

@@
